---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ovbars

<!-- badges: start -->
[![R-CMD-check](https://github.com/JanMarvin/ovbars/workflows/R-CMD-check/badge.svg)](https://github.com/JanMarvin/openxlsx2/actions)
[![r-universe](https://janmarvin.r-universe.dev/badges/openxlsx2)](https://janmarvin.r-universe.dev/ovbars)
<!-- badges: end -->

This R package allows using the `ovba` rust library to read the `vbaProject.bin` file which is included in the `xlsm` files as defined by the Office Open XML standard. The macro code is embedded in a binary OVBA file. This is readable via `ovbars`.

```{r}
fl <- "https://github.com/JanMarvin/openxlsx-data/raw/refs/heads/main/gh_issue_416.xlsm"
wb <- openxlsx2::wb_load(fl)
vba <- wb$vbaProject

code <- ovbars::ovbar_out(name = vba)
message(code["Sheet1"])

ovbars::ovbar_meta(name = vba)
```

## License

This package is licensed under the MIT license. At the moment it bundles the [`ovba`](https://github.com/tim-weis/ovba) library, which is released under the MIT License Copyright (c) 2020 Tim Weis. 
